Notes on Semi-Supervised `Novelty Detection'

### 2011-04-06 semisupervised/notes.tex
Initial commit of scrpits used to generate tables in tex about the experiments run.

\begin{table}[h]
\begin{center}
\input{simple-data/explain}
\end{center}
\caption{\label{tab:simple-distribution}Distribution used on the simple experiment.}
\end{table}

\begin{table}[h]
\begin{center}

\begin{tabular}{ |c| |c|}
\hline
$P(x|class \in know)$ & $\frac{P(x|class \in know)}{P(x)}$ \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
(kitchen, square) = 7.12 & (corridor, elongated) = 2 \\ \hline
\end{tabular}

\end{center}
\caption{\label{tab:simple-threshold}Input space sorted by threshold.}
\end{table}
\section{Experiment}
\label{sec:experiment}

>>>>

\begin{table}[h]
\begin{center}
\input{simple-data/explain}
\end{center}
\caption{\label{tab:simple-distribution}Distribution used on the simple experiment. Each column cell shows $P(feature|class)$}
\end{table}

\begin{table}
\centering
\subfloat[Input space sorted by threshold $P(x|class \in known)$]{\input{simple-data/density_threshold}}
\qquad
\subfloat[Input space sorted by threshold $P(x|class \in known)/P(x)$]{\input{simple-data/semi_threshold}}
\caption{\label{tab:simple-data-sorted}Input space sorted by threshold functions.}
\end{table}

\begin{comment}
\begin{table}
\centering
\begin{minipage}[b]{0.4\textwidth}\centering
  \input{simple-data/density_threshold}
\end{minipage}
\begin{minipage}[b]{0.4\textwidth}\centering
  \input{simple-data/semi_threshold}
\end{minipage}

\caption{Input space sorted by threshold functions.}
\end{table}
\end{comment}

As possible to see in \autoref{tab:simple-data-sorted} the access to unlabelled data allowed the system to better

\section{Experiment}
\label{sec:experiment}
